|

### 2020-09-22 coverletter.Rmd
cover letter tweak

The paper discusses the clumping of high-dimensional data points near the center of low-dimensional projections, and proposes a new algorithm to reverse the effect. We introduce a radial transformation for data points projected onto a 2D plane that is informed by the relative projected volume. The resulting display is useful for exploratory analysis in clustering or classification tasks, or to reveal features hidden near the center of a distribution, as demonstrated in the applications. It is especially beneficial in a dynamic display as obtained with tour methods, and the new visualization is available in the "tourr" package.

>>>>

The paper discusses the problem of central clumping of data points in low-dimensional projections of high-dimensional data, and proposes a new algorithm to reverse the effect. We introduce a radial transformation for data points projected onto a 2D plane that is informed by the relative projected volume. The resulting display is useful for exploratory analysis in clustering or classification tasks, or to reveal features hidden near the center of a distribution, as demonstrated in the applications. It is especially beneficial in a dynamic display as obtained with tour methods, and the new visualization is available in the "tourr" package.
